Automated Topic Naming

### 2011-09-06 ese/ese.tex
global both issues

We noticed that occasionally the names of modules would conflict with words related to other non-functional requirements. 
For instance, optimizers are very common modules in database systems: both MySQL and MaxDB have optimizer modules. 
In MySQL the optimizer is mentioned but often the change addresses  correctness or another quality. 
Despite this difference, the name of the module could fool our learners into believing the change was always about \emph{efficiency}. 
In these cases the advantages of tailoring topic names to specific project terminologies are more clear. 
Project specific word-lists would avoid automated mistakes due to the names of entities and modules of a software project.

@@

Very rarely did \textsf{exp2} and \textsf{exp3} (semi-unsupervised word matching) ever perform as well as the supervised machine learners. 
For MaxDB, \textit{reliability} was slightly better detected using the static word list of \textsf{exp2}. 
In general, the machine learners and \textsf{exp3} did better than \textsf{exp2} for both MaxDB and MySQL. 
For both MySQL and MaxDB \textit{usability} was better served by \textsf{exp2}. 
\textit{Usability} was a very infrequent label, however, which made it difficult to detect in any case.

@@

With ROC values ranging from $0.6$ to $0.8$ we can see there is promise in these methods.
\textsf{exp2} and \textsf{exp3} both indicate that static information can be used to help label topics without any training whatsoever. 
MySQL and MaxDB's machine learners made some decisions based off a few shared words: \textsf{bug, code, compiler, database, HP UX, delete, memory,
missing, problems, removed, add, added, changed, problem, and test}. 
Adding these words to the word-lists of \textsf{exp2} and \textsf{exp3} could improve performance while ensuring they were only domain specific.

>>>>

We noticed that occasionally the names of modules would conflict with words related to other non-functional requirements. 
For instance, optimizers are very common modules in database systems:
all three projects, MySQL, MaxDB, and PostgreSQL have optimizer modules. 
In MySQL the optimizer is mentioned but often the change addresses  correctness or another quality. 
Despite this difference, the name of the module could fool our learners into believing the change was always about \emph{efficiency}. 
In these cases the advantages of tailoring topic names to specific project terminologies are more clear. 
Project specific word-lists would avoid automated mistakes due to the names of entities and modules of a software project.

@@

Very rarely did \textsf{exp2} and \textsf{exp3} (semi-unsupervised word matching) ever perform as well as the supervised machine learners. 
For MaxDB, \textit{reliability} was slightly better detected using the static word list of \textsf{exp2}. 
In general, the machine learners and \textsf{exp3} did better than
\textsf{exp2} for MySQL and MaxDB, yet for PostgreSQL the
\textsf{exp2} wordlists performed better.
For both MySQL and MaxDB \textit{usability} was better served by \textsf{exp2}. 
\textit{Usability} was a very infrequent label, however, which made it difficult to detect in any case.

@@

With ROC values ranging from $0.6$ to $0.8$ for MySQL and MaxDB and
$0.47$ to $0.6$ for PostgreSQL ,we can see there is promise in these methods.
\textsf{exp2} and \textsf{exp3} both indicate that static information can be used to help label topics without any training whatsoever. 
MySQL and MaxDB's machine learners made some decisions based off a few shared words: \textsf{bug, code, compiler, database, HP UX, delete, memory,
missing, problems, removed, add, added, changed, problem, and test}. 
Adding these words to the word-lists of \textsf{exp2} and \textsf{exp3} could improve performance while ensuring they were only domain specific.
